Some forms of uncertainty may suppress the evolution of social learning

### 2022-04-08 ms.tex
added intra-/inter-generational dynamics figure

>>>>

\begin{figure}
  \centering
    \includegraphics[width=0.95\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
  \caption{Model dynamics are composed of two major parts: first, agents perform
  behaviors for $M$ time steps in a single generation. Then agents reproduce
  randomly, with more successful agents being more likely to reproduce. Newly
  ``born'' social learner agents use success bias to select and learn from a chosen
  teacher. Then, all agents from the previous generation die off, all new agents
  begin a new generation, and the process continues until 1000 total time steps
  have elapsed. At model initialization all agents are ``blank slates''.}
  \label{fig:IntraInterGenerationalDynamics}
\end{figure}
